ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-05-06 paper.tex
Merged sections

\begin{abstract}
  The ActiVis project aims to deliver a system for a mobile device that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
  To do so, it uses new developments in object detection methods, mobile computing, action generation and human-computer interfacing to interpret the user's surroundings and present useful guidance directions.
  Our approach to action generation used a Markov Decision Process (MDP) to track the system's state and output the next best location to investigate to find a target object and has been shown to work in principle in~\cite{lock2019active}.
  This work expands upon that by adding an object detector and adapting the decision-making process accordingly, providing a complete object search and guidance pipeline.
  The improved ActiVis system was evaluated in a set of experiments and it outperformed the baseline, unguided case.
  \keywords{Active vision, vision impairment, object detection}
\end{abstract}

@@

Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and human controller in Sections~\ref{sec:active-vision} and~\ref{sec:human-controller} respectively. 
The experiments that were conducted in this work and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.

@@

In this case, the error, $e$, is defined as the difference between the desired object and the object currently within view. 
The implication of adding a human into the loop is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
%These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}

Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector's classification errors that influence the action that \emph{K} generates. 
In our previous work, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and implement a POMDP that can handle classification uncertainties in object detectors and classifiers.

\section{Human Controller}\label{sec:human-controller}

The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
%A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.

@@

SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
\end{figure}

>>>>

\begin{abstract}
  The ActiVis project aims to deliver a mobile system that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
  For this, it uses new developments in object detection, mobile computing, action generation and human-computer interfacing to interpret the user's surroundings and present effective guidance directions.
  Our approach to direction generation uses a Markov Decision Process to track the system's state and output the optimal location to investigate and has been shown to work~\cite{lock2019active}.
  This work adds an object detector and adapts the guidance process accordingly to provide a complete object search and guidance pipeline.
  The improved ActiVis system was evaluated in a set of experiments and outperforms the baseline, unguided case.
  \keywords{Active vision, vision impairment, object detection}
\end{abstract}

@@

Section~\ref{sec:previous-work} discusses relevant previous work, followed by a description of the active vision system and controller in Section~\ref{sec:active-vision}.
The experiments that were conducted in this work and their results are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.

@@

%The error, $e$, is defined as the difference between the desired object and the object currently within view. 
Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge is that a person may interpret \emph{u} in any unpredictable way that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
The object detector's classification errors, \emph{n}, is added to the feedback loop as a noise signal and affects \emph{K}'s output.

In our previous work~cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
The design and implementation of this controller are discussed next.

%\section{Human Controller}\label{sec:human-controller}

%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
%It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
%The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
%A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.

@@

SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
The full SSD model achieves a slightly higher mAPs (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
%Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
\end{figure}
